Designing Types for R, Empirically

### 2020-10-16 paper/main.tex
formatting
minor

 Another interesting entry in Table~\ref{tbl:fail-breakdown-0-kaggle}
 is the fifth row, where a \CLASS{{\tt ixforeach, iter}} is being
 passed to an argument expecting a long union of classes, each of the
 form \CLASS{{\tt X, iter}}.  This is likely an instance where the
 user defined their own class, {\tt ixforeach}, and wanted to use the
 \code{iterators} package (the user called \code{iterator::iter} with
 a \CLASS{{\tt ixforeach}}, and it gained the class {\tt iter} on
 return).  As we mentioned, accounting for object-orientation in the
 type system is beyond the scope of this work, and such an inclusion
 would allow us to better type situations like this.

>>>>

 Another interesting entry in Table~\ref{tbl:fail-breakdown-0-kaggle}
 is the fifth row, where a \CLASS{{\tt ixforeach, iter}} is being
 passed to an argument expecting a long union of classes, each of the
 form \CLASS{{\tt X, iter}}.  This is likely an instance where the
 user defined their own class, {\tt ixforeach}, and wanted to use the
 \code{iterators} package (the user called \code{iterator::iter} with
 a \CLASS{{\tt ixforeach}}, and it gained the class {\tt iter} on
 return).  As mentioned, accounting for object-orientation in the
 type system is beyond the scope of this work, and such an inclusion
 would allow us to better type situations like this.
